A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-28 sections/Overview.tex
blue -> underline

Take the following worklist as an example
$$\al \Vdash \blue{(\lam x)~() \To_a a \le \al} , x:\al, \bt \Vdash \blue{\al \le \bt} \Vdash \blue{\bt \le 1}$$
There are three (blue-colored) judgment chains in the worklist,
where the first and second judgment chains (from the right) are two subtyping judgments,
and the third judgment chain, $(\lam x)~() \To_a a \le \al$,
is a sequence of an inference judgment followed by a subtyping judgment.

The algorithm first analyses the two subtyping judgments and
will find the best solutions $\al = \bt = 1$
(please refer to Figure~\ref{fig:alg} for detailed derivations).
Then we substitute every instance of $\al$ and $\bt$ with $1$,
so the variable declarations can be safely removed from the worklist.
Now we reduce the worklist to the following state
$$\nil \Vdash \blue{(\lam x)~() \To_a a \le 1}, x:1$$
which has a term variable declaration as the top element.
%Because no judgments before the declaration refer to $x$,
%as a basic property of an ordered context
%(Figure~\ref{fig:alg:syntax} shows its well-formedness criteria),
%we remove all declarations before the first judgment chain to collect unused variables.
%As a result all garbage variables are collected
%once the judgment chains refering to them are processed,
%just as what we have mentioned above about the scope tracking.
After removing the garbage term variable declaration from the worklist, we process the last remaining judgment chain,
namely an inference judgment $(\lam x)~()\To~?$, with the unit type $1$ as its result.
Finally the last judgment becomes $1 \le 1$, a trivial base case.

>>>>

Take the following worklist as an example
$$\al \Vdash \underline{(\lam x)~() \To_a a \le \al} , x:\al, \bt \Vdash \underline{\al \le \bt} \Vdash \underline{\bt \le 1}$$
There are three (underlined) judgment chains in the worklist,
where the first and second judgment chains (from the right) are two subtyping judgments,
and the third judgment chain, $(\lam x)~() \To_a a \le \al$,
is a sequence of an inference judgment followed by a subtyping judgment.

The algorithm first analyses the two subtyping judgments and
will find the best solutions $\al = \bt = 1$
(please refer to Figure~\ref{fig:alg} for detailed derivations).
Then we substitute every instance of $\al$ and $\bt$ with $1$,
so the variable declarations can be safely removed from the worklist.
Now we reduce the worklist to the following state
$$\nil \Vdash \underline{(\lam x)~() \To_a a \le 1}, x:1$$
which has a term variable declaration as the top element.
%Because no judgments before the declaration refer to $x$,
%as a basic property of an ordered context
%(Figure~\ref{fig:alg:syntax} shows its well-formedness criteria),
%we remove all declarations before the first judgment chain to collect unused variables.
%As a result all garbage variables are collected
%once the judgment chains refering to them are processed,
%just as what we have mentioned above about the scope tracking.
After removing the garbage term variable declaration from the worklist, we process the last remaining judgment chain,
namely an inference judgment $(\lam x)~()\To~?$, with the unit type $1$ as its result.
Finally the last judgment becomes $1 \le 1$, a trivial base case.
